---
title: "group_25_package"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{group_25_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library('CD25')
```

```{r}
devtools::install_github("rforbiodatascience24/group_25_package")
library('CD25')
```

# Introduction

This package can be used to replicate the central dogma of molecular biology: DNA –\> RNA –\> protein.

## Function 1

This function generates a DNA sample of wanted length.

Example usage:

```{r}
initial_name_sampling(10)
```

sampler(10)

Expected output: ('AGCTAGTCAG')

## Function 2

dna_to_rna function takes an DNA sequence as an input and returns an RNA sequence.

```{r}
dna_to_rna('AAGGTTCCTT')
```

Example usage:

rna_to_dna("ATGCGATA")

Expected output: ("AUGCGAUA")

## Function 3

This function extracts codons (triplets of characters) from a given DNA or RNA sequence, starting from a specified position.

Example usage: extract_codons("ATGCGATAGCTA", start = 1)

Expected output: c("ATG", "CGA", "TAG")

Example usage: extract_codons("ATGCGATAGCTA", start = 2)

Expected output: c("TGC", "GAT", "AGC")

## Function 4

Functions that translate codons to amino acids to create an amino acid sequence.

Input: A character vector of codons (e.g., c("AUG", "UUU", "GGC")).

Output: A string representing the translated protein sequence.

Example usage: translate_codons(c("AUG", "UUU", "GGC"))

Expected output: "MFG"

Example usage: translate_codons(c("UUU", "UCU", "UAU"))

Expected ouput: "FSY"

## Function 5

# Combining the functions

Replicating the central dogma using all 5 functions
