---
title: "group_25_package"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{group_25_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library('CD25')
```

```{r}
devtools::install_github("rforbiodatascience24/group_25_package")
library('CD25')
```

# Introduction

This package can be used to replicate the central dogma of molecular biology: DNA –\> RNA –\> protein.

## Function 1: sampler

This function generates a DNA sample of wanted length.

Example usage:

```{r}
sampler(10)
```

## Function 2: dna_to_rna

dna_to_rna function takes an DNA sequence as an input and returns an RNA sequence.

```{r}
dna_to_rna('AAGGTTCCTT')
```

## Function 3:

This function extracts codons (triplets of characters) from a given DNA or RNA sequence, starting from a specified position.

```{r}
extract_codons("ATGCGATAGCTA", start = 1)
```

```{r}
extract_codons("ATGCGATAGCTA", start = 2)
```

## Function 4: translate_codons

Function that translate codons to amino acids to create an amino acid sequence.

```{r}
translate_codons(c("AUG", "UUU", "GGC"))
```

# Function 5: Nucleotide_count_plot

This function takes a DNA or RNA sequence as input and produces a bar plot showing the counts of each nucleotide in the sequence.

```{r}
Nuc_seq <- "AGCTTAGG"
Nucleotide_Counts(Nuc_seq)
```

# Combining the functions

Replicating the central dogma using all 5 functions

```{r}

```
