---
title: "group_25_package"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{group_25_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CD25)
```

<<<<<<< HEAD
## Function 1

## Function 2
dna_to_rna function takes an DNA sequence as an input and returns an RNA sequence.

# # Example usage
#' rna_to_dna("ATGCGATAGCTA")
#' # Expected output: ("AUGCGAUAGCUA")

## Function 3

This function extracts codons (triplets of characters) from a given DNA or RNA sequence, starting from a specified position.

Example usage of the function: 
#' # Example usage
#' extract_codons("ATGCGATAGCTA", start = 1)
#' # Expected output: c("ATG", "CGA", "TAG")
#'
#' extract_codons("ATGCGATAGCTA", start = 2)
#' # Expected output: c("TGC", "GAT", "AGC")

## Function 4

Functions that translate codons to aminoacids to create an aminoacid sequence. 
Input: A character vector of codons (e.g., c("AUG", "UUU", "GGC")).
Output: A string representing the translated protein sequence.
Examples:
translate_codons(c("AUG", "UUU", "GGC")) --> "MFG"
translate_codons(c("UUU", "UCU", "UAU")) --> "FSY"

## Function 5
=======
# Function 2

dna_to_rna function takes an DNA sequence as an input and returns an RNA sequence.

# Function 1

